Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-04-27 ProbabilisticCoherence.tex
Slight restructure of 5, write up of univariate and multivariate scores in general

\todo{Discuss log score, energy (inc. non-Euclidean?) score and variogram score in general}

Table~\ref{table:scoringrules} summarizes a few existing proper scoring rules.

@@

\todo{Summary: Log score should not be used.  Energy score - still trying to prove that reconciled dominates unreconciled, will show "half" proof if necessart. Variogram score - it might be possible to show reconciled dominate unreconciled, I will have a look.}

Even though the log score can be used to evaluate simulated forecast densities with large samples \citep{Jordan2017}, it is more convenient to use if we can assume a parametric forecast density for the hierarchy. However, the degeneracy of coherent forecast densities is problematic when using log scores. We will discuss this further in the next subsection.

For the energy score with $\alpha=2$, it can be easily shown that
\begin{equation} \label{eq:(5.1)}
\text{ES}(\breve{\bm{Y}_{T+h},y_{T+h}}) = \|\bm{y}_{T+h}-\breve{\bm{\mu}}_{T+h}\|^2,
\end{equation}
where $\breve{\bm{\mu}}_{T+h} =\E_{\bm{F}}(\breve{\bm{Y}}_{T+h}) $. Therefore, in the limiting case, the energy score only measures the accuracy of the forecast mean, and not the entire distribution. Similarly, \citet{Pinson2013a} argued that the energy score given in Table~\ref{table:scoringrules} has a very low discrimination ability for incorrectly specified covariances, even though it discriminates the misspecified means well.

@@

>>>>

While the a number of alternative proper scoring rules are available for univariate forecasts, the multivariate case is somewhat more limited.  Here we focus on three cases, the log score, the energy score and the variogram score.  These are summarised in table~\ref{table:scoringrules} summarizes a few existing proper scoring rules.

@@

The log score can be approximated using a sample of values from the probabilistic forecast density \citep{Jordan2017} however it is more commonly used when a parametric form for the density is available for the probabilistic forecast.  So far, we have only defined probabilistic forecasts in terms of probability measures.  Although densities can be obtained for both reconciled and unreconciled forecasts, the degeneracy of reconciled forecasts is problematic when using log scores. We will discuss this further in the next subsection.

The energy score on the other hand can be defined in terms of the characteristic function of the probabilistic forecast, but the representation in Table~\ref{table:scoringrules} in terms of expectations leads itself to easy computation when samples from the probabilistic forecast are available. 
An interesting case is where $\alpha=2$, where it can be easily shown that
\begin{equation} \label{eq:(5.1)}
\text{ES}(\breve{\bm{Y}_{T+h},y_{T+h}}) = \|\bm{y}_{T+h}-\breve{\bm{\mu}}_{T+h}\|^2,
\end{equation}
where $\breve{\bm{\mu}}_{T+h} =\E_{\bm{F}}(\breve{\bm{Y}}_{T+h}) $. In this limiting case, the energy score only measures the accuracy of the forecast mean, and not the entire distribution and the energy score is proper, but not strictly proper. \citet{Pinson2013a} also argues that the energy score has very low discriminative ability for incorrectly specified covariances, even though it discriminates the misspecified means well.

@@

To be discussed: Energy score - still trying to prove that reconciled dominates unreconciled, will show "half" proof if necessary. Variogram score - it might be possible to show reconciled dominate unreconciled, I will have a look.
